\chapter{Analysis}\label{chap:analysis}

In our problem statement in \Cref{sec:researchstatement}, 
we asked what we can do with wearables in a smart home setting.
In the sections before that, 
we described some of the ways of controlling a smart home. 
One of these was using gestures to control devices in the home. 
As the most used sensor in wearables is the accelerometer (see \Cref{fig:wearables-sensors}), 
it makes sense to utilize this sensor to perform the gestures used to control the devices. 
Our approach to our problem statement is thus using a wearable, 
and its sensors, to perform gestures and thereby control a smart home. 

The goal of our project is to create a system, 
that allows gesture-based communication between the user and smart devices.
We described the context and the target group of this system in \Cref{sec:scenario,sec:target-group}.
We want to design a system so that a user, wearing a \emph{wrist wearable}, 
can simply point at a smart device, 
and perform a gesture to control this device. 
This is much like the solution that Reemo (see \Cref{sec:smarthomecontrol}) uses. 
However, we feel that the line-of-sight requirement is a big loss of control, 
as it severely limits the control of objects.
With a line-of-sight requirement, 
it is impossible to control objects in other rooms, 
such as turning on your coffee machine while you are in your bedroom. 
We want to remove this limitation in our solution. 

This chapter analyses the core concepts involved in creating the solution.
Gesture recognition is a important in our project, 
and will be covered in \Cref{sec:gesturerecognition}. 
In order to find the device the user is pointing at,
we need to know the user's and the devices' locations, 
as well as the user's orientation. 
\Cref{sec:analysis:orientation} describes how we find a device based on the locations. 
To find the locations, we utilize indoor location described by \Cref{sec:analysis:indoor-positioning}.

\input{content/analysis/gesture-recognition}
\input{content/analysis/orientation}
\input{content/analysis/indoor-positioning}
%%% Local Variables:
%%% mode: latex
%%% TeX-master: "../master"
%%% End:
