\chapter{Implementation}\label{chap:implementation}
%\input{content/implementation/prototypes}
This chapter describes the implementation details of our system, 
designed in \Cref{chap:design}. 
The system consists of three layers, as described by \Cref{fig:architecture}.
We designed the first layer to consist of a wearable device and a smartphone. 
However, since we did not have access to a wearable device, 
we have implemented the first layer entirely as a iPhone application. 

This application have been developed through several prototypes. 
The first prototype, described in \Cref{sec:implementation:prototypes:prototype1}, was implemented as an Android application, 
to develop a way to find which devices the user points at. 
\Cref{sec:implementation:prototypes:prototype2} describes the second prototype was implemented as a iPhone application,
developed to test communication with the server and control of the devices. 
We also developed a very basic server for this prototype, \ie the second layer. 
The third prototype in \Cref{sec:implementation:prototypes:prototype3}, 
implemented the \$3 Gesture Recognition system,
and used the location estimated from the Estimote SDK. 
The fourth and final prototype described in \Cref{sec:implementation:prototypes:prototype4} connected all the layers of the system. 
This prototype connects to and communicates with the implemented server and smart hub. 

The implementation of the server, \ie the second layer of the system, 
is described in \Cref{sec:serverimplementation}. 
As the smart hub, the third layer, is not something that we have implemented ourself, 
we will not describe the implementation of this.
However, \Cref{sec:serverimplementation} describes how it is connected to our system. 

\input{content/implementation/prototype1}
\FloatBarrier
\input{content/implementation/prototype2}
\FloatBarrier
\input{content/implementation/prototype3}
\FloatBarrier
\input{content/implementation/prototype4}
\FloatBarrier
\input{content/implementation/server}