\section{Indoor Positioning}\label{sec:indoor-positioning}
One of the most discussed or wanted features in an automated smart home is having the smart home detect where you are.
There are multiple use cases for this feature, not only in smart homes, but also in a lot of other settings. 
A few examples of where indoor positioning, or location, can be useful:
\begin{enumerate}
    \item Indoor navigation (\eg in large publics buildings such as airports or hospitals)
    \item Tracking of patients in \eg hospitals or elderly care facilities
    \item Finding lost objects such as keys in a home
    \item Tracking people in smart homes to execute certain actions when a person is near an object or an area
\end{enumerate}

%Something about Estimote
The remainder of this section will be an analysis of commercialized products that offer indoor location.
Only solutions intended for indoor positioning are considered.
GPS is not considered a potential solution as GPS is meant for outdoor positioning and the location offered by GPS tend to have poor accuracy indoors.
It will be chosen based on availability, price, easy of use, accuracy and development options.
 
\Cref{tbl:indoor-positioning} shows the results of the analysis. 
\begin{table}[!htb]
    \begin{description}[style=multiline,leftmargin=2.5cm]
        \item[Product:] Estimote Beacons and Stickers \cite{estimote}
        \item[Availability:] Beacons and Stickers are shipping. SDKs available.
        \item[Technology:] iBeacon protocol.
        \item[Price:] \$99 for beacons. \$99 for 10 stickers, one per device to be positioned.
        \item[Ease of use:] Initial installation of beacons. Attach each sticker to device.
        \item[Accuracy:] Unknown. Desired to be less than five meters. \\ \todo[author=Simon]{Update after conducting tests.} 
        
        \item[Product:] Pozyx \cite{pozyx}
        \item[Availability:] Available for preorder.
        \item[Technology:] Ultra-wideband (UWB).
        \item[Price:] \$368 for anchors. \$123 for each device to be positioned, plus supported Arduino.
        \item[Ease of use:] Initial installation of anchors. One tag for each device, plus supported Arduino. Not meant for mounting.
        \item[Accuracy:] Claimed to be 10 cm. Untested. \\
        
        \item[Product:] SmartActionSLAM \cite{SASLAM}
        \item[Availability:] Android Application (research). Not commercialized.
        \item[Technology:] Smartphone sensors.
        \item[Price:] N/A.
        \item[Ease of use:] Requires modification of source code (available) to get real-time position. 
        \item[Accuracy:] Reported to have a mean error of 0.34m (only using smartphone and no external sensors).
    \end{description}
    \todo[author=Thalley]{Can we find more?}
    \caption{Assessment of potential solutions for indoor positioning. Please note that all prices are converted to U.S. dollars from their respective currency. Prices include the minimum available hardware for positioning a device.}
    \label{tbl:indoor-positioning}
\end{table}

Estimote gives a solution using Bluetooth low energy (BLE) beacons with the iBeacon protocol. 
The beacons can be mounted on walls in a room or building, 
and then by using the round trip time of the signals to each beacon, it can estimate where the user is. 

Pozyx is uses a wireless radio technology known as ultra-wideband, which works much like BLE but at a different frequency. 
Like Estimote, it also requires setting up ``anchors'' and then using the round trip time to find the location. 
It is currently only for Arduinos. 

SmartActionSLAM is an Android application from research done by Hardegger \etal \cite{SASLAM}. 
This solution is a lot different from most other indoor location solutions. 
It \emph{calculates} an estimated location by counting steps and estimating step length and direction. 
In theory it can be adapted to almost any smartphone, 
but requires a lot of work to adapt the released code from the research project. 