\section{Initial Problem}\label{sec:initproblem}
%Thalley: Første source kan også laves som en fin graf hvis ønsket. Brug tal fra: http://www.statista.com/statistics/259372/wearable-device-market-value/
Wearable technology is a trending form of technology as of 2015 \cite{WEARABLESTREND}. 
As the name implies, wearables are devices that, unlike most electronics, are worn by the user. 
The most common type of wearables today are smartwatches, 
\ie watches that run an advanced operating system and can perform more actions that regular watches, 
such as communicating with a smartphone or other smart devices.
Another popular wearable are smart-wristbands which usually tracks activity, 
among other things, and sends this data to a connected smartphone via an application. 
Smartphones are usually not considered a wearable since they are \emph{carried} and not \emph{worn}. 

The increasing trend in wearables is likely due to increased computational power in small devices and decreased sizes of sensors, 
which allows more power and functionality to wearables devices. 
The increasing trend, as well as better wearables devices, 
opens up new possibilities since we can now carry more computational power with us on the go, 
that we can utilize to perform actions that we could not before, 
or perform other actions faster or better. 
An example of this is that we can now track our level of activity together with our location to analyze ourselves, 
or even automate actions based on our location, mood or even health. 

Another trend that utilizes IoT is smart homes.
Smart homes are homes that are to some degree automated by utilization IoT devices. 
The devices used for smart homes differ greatly from wearables as they are usually stationary. 
The concept of smart homes have been around for a while and numerous homes have already integrated some of these smart devices. 
An extreme example of a high-end smart home is Bill Gate's mansion in Medina, Washington \cite{billgatehouse}.
This \$100 million house have sensors to adjust each room's temperature and lighting, 
and have speakers behind the wallpaper that follows you from room to room. 
The artwork in the house is mostly digital and can be changed by pressing a button. 
One can only imagine what other technology is being used in that house. 

With these increasing technology trends in wearables and smart homes, 
it could be very interesting to see how and if we can integrate these. 
For example could it be interesting to see if we can use wearables as a form of control of smart homes, 
or maybe even use wearables to automate the smart homes.
We will in the following sections look into the current state of wearables and smart homes, 
and investigate if we can integrate them. 
