\section{Indoor Positioning}

There are two distinct ways of locating a user when using the iBeacon protocol \cite{estimote:monitoring-ranging}.

\begin{itemize}
\item Region monitoring is performed to check if a user enters or leaves a specific region. A region is a geofence, \ie a virtual perimeter around some location. A region can be used to check if a user arrives or leaves his house, his workplace or if he is nearby a shop encapsulated in a geofence. Regions are useful for performing simple home automation, \eg turn the lights on when the user arrives at home and turn them off when they leave.
\item Ranging is more granular than region monitoring and is used to continuously retrieve the set of beacons in range, along with an estimated distance to them based on the signal strengths. Ranging is used to get a granular user position.
\end{itemize}

According to both Apple and Estimote it is preferred that ranging is only performed while the application is in the foreground, 
\ie the application is on the screen and the user is likely to interact with the application. 
The reason for this is that ranging for beacons can have a negative impact on the battery life, 
whereas the region monitoring does not use as much battery power.

While Apple and Estimote advise against performing beacon ranging in the background, it is possible \cite{apple:monitoring-ibeacon} \cite{estimote:monitoring-ranging}.

\input{content/design/configuration-of-locations}

%%% Local Variables:
%%% mode: latex
%%% TeX-master: "../../master"
%%% TeX-command-extra-options: "-shell-escape"
%%% End:
